We are not the 99 percent: the Local Group as an extreme outlier in satellite distributions

### 2017-10-28 paper/paper.tex
abstract titulo

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG as an outlier]{We are not the 99 percent: the Local Group as an
  outlier in galaxy pairs' satellite distributions}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\begin{abstract}
In this paper we quantify the joint spatial distribution of the brightest satellites
around the Milky Way (MW) and M31, the dominant galaxies in the Local
Group (LG).
We use the Illustris-1 and ELVIS simulations to quantify how the 
unusual satellite distribution in the MW  makes the LG an atypical pair.
A crucial aspect in our analysis is that we define the atypicallity as
the degree at which a satellite distribution deviates from sphericity and
not as a deviation from simulations.
We find that only $0.05\%$ to $0.25\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of atipicality, making
the LG a $3\sigma$ outlier.
\end{abstract}

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG as an outlier]{We are not the 99 percent: the Local Group as an
  extreme outlier in satellite distributions}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\begin{abstract}
In this paper we quantify the joint spatial distribution of the
brightest satellites around the Milky Way (MW) and M31, the dominant
galaxies in the Local Group (LG).
We use the Illustris-1 and ELVIS simulations to quantify the
expected deviations from statistically spherical satellite
distributions in the Lambda Cold Dark Matter paradigm. 
We estimate that only $0.05\%$ to $0.25\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree deviation form
sphericity, making the LG a $3\sigma$ outlier.  
\end{abstract}
